Results

### 2018-11-23 Manuscript_draft/Results.Rmd
NMDS

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
library(reshape2)
library(ape)
library(phytools)
library(plotrix)
library(dplyr)
#load environment
load("myEnvironment_mantel.RData")
```

@@

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
library(reshape2)
library(ape)
library(phytools)
library(plotrix)
library(dplyr)
library(ggfortify)
library(ggplot2)
library(stats)
library(cluster)
#load environment
load("myEnvironment_mantel.RData")
```

@@

\newpage
Multivariate homogeinity of groups dispersions (variances). Non-euclidean distances are handle by reducing the original distances to principal coordinates. Here I present an analysis of the variances for the measurements of Gynoecium for the ten species. The measurements used are width and length of stigma, style and ovary.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
load("betadisper.RData")
plot(traits, cex=1,pch=10:21,
     main="Gynoecium:MDS coordinates", cex.lab=1.25,label.cex=0.5,
     xlab=labs[1], ylab=labs[2], ylim=c(-0.35,0.35),xlim=c(-0.35,0.35),
     hull=FALSE, ellipse=TRUE, conf=0.68, lwd=2)

\newpage
Other way of showing the same results but now with Principal Components Analysis. Maybe is more elegant? Grouped by species.

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
load("betadisper.RData")
autoplot(prcomp(all_pca), data = traits_all, colour = 'species', frame = TRUE, frame.type = 'norm')
```

\newpage
Now I group by family

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
load("betadisper.RData")
autoplot(prcomp(all_pca), data = traits_all, colour = 'family', frame = TRUE, frame.type = 'norm', main="Gynoecium spp PCA")
```
